\section{Physical model}\label{sec:pm}

Electrohydrodynamics involves the study of electric phenomena on fluid
flow. How fluids carrying electrical charges (electrolytes) react upon
external electrical fields or interact with charged objects are
examples of problems that arise in this field. 

As a charged object is brought into contact with an electrolyte it is,
qualitatively, easily deduced that ions with a sign of charge opposite
to that of the object will be attracted to the object and ions with
the same sign of charge will be repelled. These two distinct
categories of ions will from hereon be referred to as counter- and
co-ions respectively. In this case, for a neutral electrolyte, a
surplus of counter-ions will be present in the direct vicinity of the
object and a surplus of co-ions will be present at some other location
further from the object. The part of the net charged fluid nearest to
the charged boundary is often referred to as an electrical double
layer (EDL) \cite{dongquing-ren-book}. 

Traditionally, the physical description of EDLs and electrokinetics in
general is based on the Poisson-Boltzmann model. However the PB model
includes some crude assumptions on the system and is sometimes not an
accurate choice, see section \ref{sec:et:pb} for a brief
description. Therefore, more sophisticated modelling approaches has
been proposed e.g. in \cite{}. This paper is based on such an approach
which is described further in this section.

\input{physical_model/pm_coupling.tex}

\input{physical_model/pm_poisson.tex}

\input{physical_model/pm_np.tex}
\input{physical_model/pm_pb.tex}

\input{physical_model/pm_navier.tex}

\input{physical_model/pm_electrovis.tex}

\input{physical_model/pm_electroosmosis.tex}

%lite intro

%börja inte med allmän teorpmisk formulering

%sedan lite resultat, double layers

%pressure driven flows...
